---
title: "CNVxplorer report"
author: "Vignette Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



## 1. Clinical information

```{r echo= FALSE, comment = NA, message=FALSE}

params$name
params$sex
params$age
params$comment

```

## 2. Input data

```{r echo= FALSE, comment = NA, message=FALSE}



size_cnv <- params$end - params$start + 1

def_variable <- c('Chromosome', 'Start interval:', 'End interval:', 'Size:', 'Nº of genes:')
def_value <- c(params$chrom, params$start, params$end, paste(size_cnv, 'bp'), nrow(data_selected()))

df_tmp <- tibble('Variable' = def_variable, 'Value' = def_value)
knitr::kable(df_tmp)

```


## 2. Comparison size

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

      start_coordinates <- coord_user()[1]
      end_coordinates <- coord_user()[2]
      
      size_cnv_query = end_coordinates - start_coordinates + 1
      
      cnv_df %>%
        ggplot(aes(length_cnv, y = source)) +
        stat_density_ridges(quantile_lines = TRUE, quantiles = 2, aes(fill = source), alpha = 0.6, show.legend = FALSE, size = 1.25) +
        geom_vline(aes(xintercept = size_cnv_query), linetype = 2, color = 'red', size = 1.5) +
        scale_x_log10() +
        scale_y_discrete(expand = c(0.01, 0)) +
        scale_fill_viridis_d() +
        xlab('-log10(CNVs size)') +
        ylab('Database') +
        theme_ridges()

```


## 3. Functional analysis


### 3.1 Functional profile (optional)

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

if (exists('running_go()')) {
  
  if (nrow(running_go()) > 0) {

      running_go() %>%
        as_tibble() %>%
        arrange(desc(Count)) %>%
        filter(Count != 0) %>%
        slice(1:10) %>%
        as_tibble() %>%
        # mutate(p.adjust = -log10(p.adjust)) %>%
        ggplot(aes(reorder(Description, Count), Count)) +
        geom_col(aes(fill = Description), color = 'black', show.legend = FALSE) +
        scale_fill_viridis_d() +
        coord_flip() +
        xlab('') +
        ylab('Number of genes') +
        geom_text(
          aes(label = GeneRatio, y = Count + 0.05),
          position = position_stack(vjust = 0.5),
          vjust = 0
        ) +
        theme_minimal() +
        theme(axis.text=element_text(size=12),
              axis.title=element_text(size=14,face="bold"))
    
  }
}
```



### 3.2 Gene ontology (optional)

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

if (exists('running_enrich_go()')) {
  
  if (nrow(running_enrich_go()) > 0) {
    
        running_enrich_go() %>%
          as_tibble() %>%
          mutate(p.adjust = -log10(p.adjust)) %>%
          ggplot(aes(reorder(Description, p.adjust), p.adjust)) +
          geom_col(aes(fill = Description), color = 'black', show.legend = FALSE) +
          scale_fill_viridis_d() +
          coord_flip() +
          xlab('') +
          ylab('-log10(p-adjusted)') +
          ggtitle('GO analysis') +
          geom_hline(yintercept =-log10(as.numeric(input$sign_vline)), color = 'red', alpha = 0.6, linetype = 'dashed', size = 2) +
          geom_text(
            aes(label = GeneRatio, y = p.adjust + 0.05),
            position = position_stack(vjust = 0.5),
            vjust = 0
          ) +
          theme_minimal() +
          theme(axis.text=element_text(size=12),
                axis.title=element_text(size=14,face="bold"))
        
  }
}
```


### 3.3 Pathway analysis (optional)

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

if (exists('running_path()')) {
  
  if (nrow(running_path()) > 0) {
      
        running_path() %>%
        mutate(p.adjust = -log10(p.adjust)) %>%
        ggplot(aes(reorder(Description, p.adjust), p.adjust)) +
        geom_col(aes(fill = Description), color = 'black', show.legend = FALSE) +
        scale_fill_viridis_d() +
        coord_flip() +
        xlab('') +
        ylab('-log10(p-adjusted)') +
        ggtitle('Enriched pathways') +
        geom_hline(yintercept =-log10(as.numeric(input$sign_vline_path)), color = 'red', alpha = 0.6, linetype = 'dashed', size = 2) +
        geom_text(
          aes(label = GeneRatio, y = p.adjust + 0.05),
          position = position_stack(vjust = 0.5),
          vjust = 0
        ) +
        theme_minimal() +
        theme(axis.text=element_text(size=12),
              axis.title=element_text(size=14,face="bold"))
        
  }  
}
```



### 3.4 Gene-disease association (optional)

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}


if (exists('running_do()')) {
  
  if (nrow(running_do()) > 0) {
    
    cnetplot(running_do(), foldChange= hgcn_genes$entrez_id, readable = TRUE)

        
  }     
}
```



### 3.3 Pathway analysis (optional)

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

if (exists('running_path()')) {
  
  if (nrow(running_path()) > 0) {
      
        running_path() %>%
        mutate(p.adjust = -log10(p.adjust)) %>%
        ggplot(aes(reorder(Description, p.adjust), p.adjust)) +
        geom_col(aes(fill = Description), color = 'black', show.legend = FALSE) +
        scale_fill_viridis_d() +
        coord_flip() +
        xlab('') +
        ylab('-log10(p-adjusted)') +
        ggtitle('Enriched pathways') +
        geom_hline(yintercept =-log10(as.numeric(input$sign_vline_path)), color = 'red', alpha = 0.6, linetype = 'dashed', size = 2) +
        geom_text(
          aes(label = GeneRatio, y = p.adjust + 0.05),
          position = position_stack(vjust = 0.5),
          vjust = 0
        ) +
        theme_minimal() +
        theme(axis.text=element_text(size=12),
              axis.title=element_text(size=14,face="bold"))
        
  }  
}
```



## 4. Pubmed articles associated with the region

```{r echo= FALSE, comment = NA, message=FALSE, fig.width=12}

# kable(running_pubmed()) %>%
#   kable_styling() %>%
#   scroll_box(width = "1000px", height = "500px")

datatable(running_pubmed(), 
          rownames = FALSE,
          options =
            list(pageLength = 5))
```


## Comparison size



<!-- ## 2. Gene content -->

<!-- ```{r echo= FALSE, comment = NA, message=FALSE } -->
<!-- options(width = 400) -->
<!-- library(knitr) -->
<!-- library(kableExtra) -->
<!-- # knitr::kable( data_selected()) %>% -->
<!-- #     kable_styling(full_width = F) -->
<!-- #    -->
<!-- #     # scroll_box(width = "500px", height = "200px") -->

<!-- # datatable(data_selected(), style = 'bootstrap',  -->
<!-- #           options = list(pageLength = 5, autoWidth = TRUE), width = 100) -->

<!-- ``` -->


## Stay Tuned

Please visit the [development page](http://github.com/yixuan/prettydoc/) of the 
`prettydoc` package for latest updates and news. Comments, bug reports and
pull requests are always welcome.

